Near Optimal Behavior via Approximate State Abstraction

### 2016-02-05 paper/conclusion.tex
Cleaned up some math and made citations work properly

% Future work.
There are many directions for future work.
% Learning abs functions online.
First, we are interested in extending the approach of \citeauthor{ortner2013adaptive} by learning the approximate abstraction functions introduced in this paper online in the planning or \ac{RL} setting. \dnote{Add year if possible}
% Necessary conditions.
While our work presents several sufficient conditions for achieving bounded error of learned behavior with approximate abstractions, we hope to investigate what conditions are strictly necessary for an approximate abstraction to achieve bounded error.
% Options/termporal abstraction
We investigated the use of options~\cite{sutton1999between} in the Taxi domain, and found a negligible difference in the degree and quality of compression compared to compression without options. In the future, we are interested in characterizing the relationship between temporal abstractions, such as those afforded by options, and approximate abstractions.
% Compressibility
Lastly, we are interested in understanding the relationship between various approximate abstractions and the information theoretical limitations on the degree of abstraction achievable in \acp{MDP}.

>>>>

% Future work.
There are many directions for future work.
% Learning abs functions online.
First, we are interested in extending the approach of \citet{ortner2013adaptive} by learning the approximate abstraction functions introduced in this paper online in the planning or \ac{RL} setting. \dnote{Add year if possible}
% Necessary conditions.
While our work presents several sufficient conditions for achieving bounded error of learned behavior with approximate abstractions, we hope to investigate what conditions are strictly necessary for an approximate abstraction to achieve bounded error.
% Options/termporal abstraction
We investigated the use of options~\cite{sutton1999between} in the Taxi domain, and found a negligible difference in the degree and quality of compression compared to compression without options. In the future, we are interested in characterizing the relationship between temporal abstractions, such as those afforded by options, and approximate abstractions.
% Compressibility
Lastly, we are interested in understanding the relationship between various approximate abstractions and the information theoretical limitations on the degree of abstraction achievable in \acp{MDP}.

### 2016-02-05 paper/introduction.tex
Cleaned up some math and made citations work properly

% Abstraction is a good idea b/c MDP has poly comp comp and samp comp in S, but S grows fast.
Solving for optimal behavior in \acp{MDP} in a planning setting is known to be P-Complete in the size of the state space~\cite{papadimitriou1987complexity,littman1995complexity}. Similarly, many \ac{RL} algorithms for solving \acp{MDP} are known to require a number of samples polynomial in the size of the state space~\cite{strehl2009reinforcement}. Although polynomial runtime or sample complexity may seem like a reasonable constraint, the size of the state space of an \ac{MDP} grows super-polynomially with the number of variables that characterize the domain, a results of Bellman's curse of dimensionality. Thus, solutions polynomial in state space size are often ineffective for sufficiently complex tasks. \dnote{Would prefer a different example} For instance, a robot involved in a pick-and-place task might be able to employ planning algorithms to solve for how to manipulate some objects into a desired configuration in time polynomial in the number of states, but the number of states it must consider grows exponentially with the number of objects it is working with \enote{Cite Dabe Icaps}.

@@

% Thesis: Approximate abstraction for three reasons.
The thesis of this work is that performing approximate abstraction in \acp{MDP} by relaxing the state-aggregation criteria from equality of quantities to $\epsilon$-closeness offers three benefits while maintaining bounded error in the resulting behavior. First, approximate abstractions employ the sort of knowledge that we expect a planning or learning algorithm to compute without fully solving the \ac{MDP}. In contrast, exact abstractions often require solving for optimal behavior, thereby defeating the purpose of abstraction. Second, because of their relaxed criteria, approximate abstractions can achieve greater degrees of compression than exact abstractions. This difference is particularly important in environments where no two states are identical. \dnote{note this in empirical results discussion, that random is sort of like a natural environment and when eps is 0, no compression} Third, because the state-aggregation criteria are relaxed to near equality, approximate abstractions are able to tune the aggressiveness of abstraction by adjusting what they consider sufficiently similar states.

>>>>

% Abstraction is a good idea b/c MDP has poly comp comp and samp comp in S, but S grows fast.
Solving for optimal behavior in \acp{MDP} in a planning setting is known to be P-Complete in the size of the state space~\cite{papadimitriou1987complexity,littman1995complexity}. Similarly, many \ac{RL} algorithms for solving \acp{MDP} are known to require a number of samples polynomial in the size of the state space~\cite{strehl2009reinforcement}. Although polynomial runtime or sample complexity may seem like a reasonable constraint, the size of the state space of an \ac{MDP} grows super-polynomially with the number of variables that characterize the domain, a result of Bellman's curse of dimensionality. Thus, solutions polynomial in state space size are often ineffective for sufficiently complex tasks. \dnote{Would prefer a different example} For instance, a robot involved in a pick-and-place task might be able to employ planning algorithms to solve for how to manipulate some objects into a desired configuration in time polynomial in the number of states, but the number of states it must consider grows exponentially with the number of objects it is working with \enote{Cite Dabe Icaps}.

@@

% Thesis: Approximate abstraction for three reasons.
The thesis of this work is that performing approximate abstraction in \acp{MDP} by relaxing the state-aggregation criteria from equality of quantities to $\epsilon$-closeness maintains bounded error in the resulting behavior while offering three benefits. First, approximate abstractions employ the sort of knowledge that we expect a planning or learning algorithm to compute without fully solving the \ac{MDP}. In contrast, exact abstractions often require solving for optimal behavior, thereby defeating the purpose of abstraction. Second, because of their relaxed criteria, approximate abstractions can achieve greater degrees of compression than exact abstractions. This difference is particularly important in environments where no two states are identical. \dnote{note this in empirical results discussion, that random is sort of like a natural environment and when eps is 0, no compression} Third, because the state-aggregation criteria are relaxed to near equality, approximate abstractions are able to tune the aggressiveness of abstraction by adjusting what they consider sufficiently similar states.

### 2016-02-05 paper/related_work.tex
Cleaned up some math and made citations work properly

\subsection{Approximate State Abstraction}
\citep*{dean1997model} investigated partitioning an \ac{MDP}'s state space into $\epsilon$-homogenous blocks, which are defined as clusters of states whose transition model and reward function are within $\epsilon$ of each other. They develop an algorithm called Interval Value Iteration (IVI) that converges to the correct bounds on a family of abstracted MDPs called a Bounded MDP. This method of abstraction is effectively characterized as a function belonging to the approximate class $\phi_{model}$.
Several approaches build on the notion of $\epsilon$-homogeneity. \citep*{even2003approximate} analyzed different distance metrics used in the process of identifying $\epsilon$-homogenous partitions. \citep*{ortner2013adaptive} developed an algorithm for learning partitions in an online setting by taking advantage of the confidence bounds for $\mcT$ and $\mcR$ provided by UCRL~\cite{auer2009near}.

\subsection{Specific Abstraction Algorithms}
Many previous works have targeted the creation of algorithms that enable state abstraction for MDPs. \citep*{andre2002state} investigated a method for state abstraction in hierarchical reinforcement learning leveraging a programming language called ALISP that promotes the notion of {\it safe} state abstraction. Agents programmed using ALISP can ignore irrelevant parts of the state, achieving abstractions that maintain optimality. \citep{dietterich2000hierarchical} developed MAXQ, a framework for composing tasks into an abstracted hierarchy where state aggregation can be applied. \citep*{jong2005state} introduced a method called {\it policy-irrelevance} in which agents identify (online) which state variables may be safely abstracted away in a factored-state \ac{MDP}. The agent will learn to ignore state variables that don't impact optimal behavior. For a more complete survey of algorithms that leverage state abstraction in past reinforcement-learning papers, see \citep{li2006towards}.

@@

\citep*{li2006towards} developed a framework for exact state abstraction in \acp{MDP}. In particular, the authors defined five classes of state-aggregation functions, inspired by existing methods for state aggregation in \acp{MDP}. We generalize two of these five classes, $\phi_{Q^*}$ and $\phi_{\text{model}}$, to the approximate abstraction case. Note that when $\epsilon=0$ our generalizations are equivalent to the corresponding exact methods. Additionally, when $\epsilon=0$ our bounds indicate that no value is lost, which is one of core results of \citep{li2006towards}.

>>>>

\subsection{Approximate State Abstraction}
\citet{dean1997model} investigated partitioning an \ac{MDP}'s state space into $\epsilon$-homogenous blocks, which are defined as clusters of states whose transition model and reward function are within $\epsilon$ of each other. They develop an algorithm called Interval Value Iteration (IVI) that converges to the correct bounds on a family of abstracted MDPs called a Bounded MDP. This method of abstraction is effectively characterized as a function belonging to the approximate class $\phi_{model}$.
Several approaches build on the notion of $\epsilon$-homogeneity. \citet{even2003approximate} analyzed different distance metrics used in the process of identifying $\epsilon$-homogenous partitions. \citet{ortner2013adaptive} developed an algorithm for learning partitions in an online setting by taking advantage of the confidence bounds for $\mcT$ and $\mcR$ provided by UCRL~\cite{auer2009near}.

\subsection{Specific Abstraction Algorithms}
Many previous works have targeted the creation of algorithms that enable state abstraction for MDPs. \citet{andre2002state} investigated a method for state abstraction in hierarchical reinforcement learning leveraging a programming language called ALISP that promotes the notion of {\it safe} state abstraction. Agents programmed using ALISP can ignore irrelevant parts of the state, achieving abstractions that maintain optimality. \citet{dietterich2000hierarchical} developed MAXQ, a framework for composing tasks into an abstracted hierarchy where state aggregation can be applied. \citet{jong2005state} introduced a method called {\it policy-irrelevance} in which agents identify (online) which state variables may be safely abstracted away in a factored-state \ac{MDP}. The agent will learn to ignore state variables that don't impact optimal behavior. For a more complete survey of algorithms that leverage state abstraction in past reinforcement-learning papers, see \citet{li2006towards}.

@@

\citet{li2006towards} developed a framework for exact state abstraction in \acp{MDP}. In particular, the authors defined five classes of state-aggregation functions, inspired by existing methods for state aggregation in \acp{MDP}. We generalize two of these five classes, $\phi_{Q^*}$ and $\phi_{\text{model}}$, to the approximate abstraction case. Note that when $\epsilon=0$ our generalizations are equivalent to the corresponding exact methods. Additionally, when $\epsilon=0$ our bounds indicate that no value is lost, which is one of core results of \citet{li2006towards}.

### 2016-02-05 paper/theory_results.tex
Cleaned up some math and made citations work properly

% Q* Lemma -- lemma 1
We consider an approximate version of \citeauthor{li2006towards}'s $\phi_Q^*$, where states are aggregated together when their optimal $Q$-values are within $\epsilon$.

@@

% Proof
\textbf{Proof of Lemma~\ref{lma:Q*}:}
We first demonstrate that $Q$-values in the abstract \ac{MDP} are boundedly close to $Q$-values in the ground \ac{MDP} (Claim \ref{clm:closeQs}). We next leverage Claim \ref{clm:closeQs} to demonstrate that the optimal action in the abstract \ac{MDP} is nearly optimal in the ground \ac{MDP}  (Claim \ref{clm:optAbsActionNearOptGround}). Lastly, we use Claim \ref{clm:optAbsActionNearOptGround} to conclude Lemma \ref{lma:Q*} (Claim \ref{clm:lmaFromClm}).
% Claim 1:
\begin{clm}
\label{clm:closeQs}
Optimal $Q$-values in the abstract \ac{MDP} closely resemble optimal $Q$-values in the ground \ac{MDP}:
\begin{equation}
\label{eq:Q*Claim1}
\forall_{s_G \in \mathcal{S}_G, a} |Q_G(s_G, a) - Q_A(\epQ(s_G), a)| \leq \frac{\epsilon}{1-\gamma}.
\end{equation}
\end{clm}

@@

It follows that the $Q$-value of a state $s$ in $M^T$ for action $a$ is defined by:
\begin{equation}
Q_T(s, a) = 
\begin{cases}
	   Q_G(s, a), &  \text{if } T=0,\\
	   \underset{g \in G(s)}{\sum} \left[ \omega(g)Q_G(g,a) \right], & \text{if } T = 1,\\
	   \mathcal{R}_A(\epQ(s),a) + \sigma_{T-1}(s,a), &\text{o/w},
\end{cases}
\end{equation}
where
\begin{equation}
\sigma_{T-1}(s,a) = \gamma \underset{{s_A}' \in \mathcal{S}_A}{\sum} \mathcal{T}_A(\epQ(s),a,{s_A}') \max_{a'} Q_{T-1}({s_A}', a').
\end{equation}

We proceed by induction on $T$ to show that:
\begin{equation}
\forall_{T, s_G \in \mathcal{S}_G, a} |Q_G(s_G, a) - Q_T(s_G, a)| \leq \sum_{t=0}^{T-1} \epsilon \gamma^{t},
\end{equation}

@@

We assume as our inductive hypothesis that:
\begin{equation}
\forall_{s_G \in \mathcal{S}_G, a} |Q_G(s_G, a) - Q_{T-1}(\epQ(s_G), a)| \leq \sum_{t=0}^{T-2} \epsilon \gamma^t.
\end{equation}

Consider a fixed but arbitrary state, $s_G \in \mathcal{S}_G$, and fixed but arbitrary action $a$.
We denote $\epQ(s_G)$ as $s_A$. 
By definition of $Q_{T}(s_A, a)$, $\mathcal{R}_A$, $\mathcal{T}_A$:
\begin{multline*}
Q_T(s_A, a) = \sum_{g \in G(s_A)}\omega(g)\ \times \\ 
 \left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'} Q_{T-1}(g', a')      \right].
\end{multline*}
Applying our inductive hypothesis yields:
\begin{multline*}
Q_T(s_A, a) \leq \sum_{g \in G(s_A)}\omega(g) \times \biggl[ R_G(g,a)\ + \\ \gamma \sum_{g' \in \mathcal{S}_G} T_G(g,a,g') \max_{a'}(Q_G(g', a') + \sum_{t=0}^{T-2} \epsilon \gamma^t) \biggr].
\end{multline*}
%&\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \sum_{g \in X(s_A)}\omega(g)\left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'}Q_0      \right]\\
Then,
\begin{equation*}
Q_T(s_A, a) \leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \sum_{g \in G(s_A)}\left[ \omega(g)\ Q_G(g,a)\right].
\end{equation*}
since all aggregated states have $Q$-values within $\epsilon$ of one another:
\begin{align*}
Q_T(s_A, a) \leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \epsilon + Q_G(s_G, a). \\
\therefore\ \left| Q_{T}(s_A, a) - Q_G(s_G,a) \right| \leq \gamma\sum_{t=0}^{T-1}\epsilon \gamma^t
\end{align*}
Since $s_G$ and $s_A$ are arbitrary, we conclude
\begin{equation}
\forall_{T, s_G \in \mathcal{S}_G, a} |Q_G(s_G, a) - Q_T(\epQ(s_G), a)| \leq \sum_{t=0}^{T-1} \epsilon \gamma^t.
\end{equation}

As $T \rightarrow \infty$, $Q_T$ becomes $Q_A$ and $\sum_{t=0}^{T-1} \epsilon \gamma^t$ becomes $\frac{\epsilon}{1-\gamma}$. Therefore, Equation $\ref{eq:Q*Claim1}$ follows. \\

@@

Now, consider an approximate version of \citeauthor{li2006towards}'s $\phi_{model}$, where states are aggregated together when their rewards and transitions are within $\epsilon$.
\bdefn{$\epM$}
We let $\epM$ define a type of abstraction that, for fixed $\epsilon$, satisfies:
\begin{multline}
\epM(s_1) = \epM(s_2) \rightarrow \\
\forall_a \left| \mcR_G(s_1, a) - \mcR_G(s_2, a)\right| \leq \epsilon\; \wedge\ \\
\forall_{s_A \in \mcS_A} \left|\sum_{{s_G}' \in G(s_A)} \left[\mcT_G(s_1, a, {s_G}') - \mcT_G(s_2, a,{s_G}')\right] \right| \leq \epsilon.
\end{multline}
\edefn

@@

We consider approximate abstractions derived from a multinomial distribution over $Q^*$ for similar reasons to our motivation in considering the Boltzmann distribution. Additionally, the multinomial distribution is appealing due to its simplicity.
\bdefn{$\epMu$}
We let $\epMu$ define a type of abstraction that, for fixed $\epsilon$, satisfies
\begin{multline}
\epMu(s_1) = \epMu(s_2) \rightarrow \\
\forall_{a} \left|\frac{Q_G(s_1,a)}{\sum_b Q_G(s_1,b)} - \frac{Q_G(s_1,a)}{\sum_b Q_G(s_1,b)}\right| \leq \epsilon.
\end{multline}
\edefn
\dnote{Some explanation of what this one does}

We also assume that the difference in normalizing terms is bounded by some positive factor, $k \in \mathbb{R}$, of $\epsilon$:
\begin{equation}
\left |\sum_i Q_G(s_1,a_i) - \sum_j Q_G(s_2,a_j) \right | \leq k\epsilon.
\end{equation}
\dnote{Some explanation of why it's okay to assume this. Answer: Q magnitudes can be artbirarily off, making the denominators similar lets us say, Hm. These q magnitudes are roughly in the same ballpark.}
%zzz why is that ok? why is it useful? (overall, I think we should take a slightly more pedagogical perspective. we're not writing programs, we're writing explanations.
\begin{lma} When $S_A$ is created using a function of the $\epMu$ type, for some non-negative constant $k \in \mathbb{R}$:
\begin{equation}
\forall_{s \in S_M} V_G^{\pi^*_G}(s) - V_G^{\pi_{GA}}(s) \leq \frac{\frac{2\epsilon|\mathcal{A}|}{1-\gamma} + k \epsilon^2 + k}{(1-\gamma)^2}.
\end{equation}
\label{lma:mult_lemma}
\end{lma}

>>>>

% Q* Lemma -- lemma 1
We consider an approximate version of \citet{li2006towards}'s $\phi_Q^*$,. In our abstraction, states are aggregated together when their optimal $Q$-values are within $\epsilon$.

@@

% Proof
\textbf{Proof of Lemma~\ref{lma:Q*}:}
We first demonstrate that $Q$-values in the abstract \ac{MDP} are close to $Q$-values in the ground \ac{MDP} (Claim \ref{clm:closeQs}). We next leverage Claim \ref{clm:closeQs} to demonstrate that the optimal action in the abstract \ac{MDP} is nearly optimal in the ground \ac{MDP}  (Claim \ref{clm:optAbsActionNearOptGround}). Lastly, we use Claim \ref{clm:optAbsActionNearOptGround} to conclude Lemma \ref{lma:Q*} (Claim \ref{clm:lmaFromClm}).
% Claim 1:
\begin{clm}
\label{clm:closeQs}
Optimal $Q$-values in the abstract \ac{MDP} closely resemble optimal $Q$-values in the ground \ac{MDP}:
\begin{equation}
\label{eq:Q*Claim1}
\forall_{s_G \in \mathcal{S}_G, a} |Q_G(s_G, a) - Q_A(\epQ(s_G), a)| \leq \frac{\epsilon}{1-\gamma}.
\end{equation}
\end{clm}

@@

It follows that the $Q$-value of a state $s$ in $M^T$ for action $a$ is defined by:
\begin{equation}
Q_T(s, a) = 
\begin{cases}
	   Q_G(s, a), &  \text{if } T=0,\\
	   \underset{g \in G(s)}{\sum} \left[ \omega(g)Q_G(g,a) \right], & \text{if } T = 1,\\
	   \mathcal{R}_A(\epQ(s),a) + \sigma_{T-1}(s,a), &\text{o/w},
\end{cases}
\end{equation}
where
\begin{equation*}
\sigma_{T-1}(s,a) = \gamma \underset{{s_A}' \in \mathcal{S}_A}{\sum} \mathcal{T}_A(\epQ(s),a,{s_A}') \max_{a'} Q_{T-1}({s_A}', a').
\end{equation*}

We proceed by induction on $T$ to show that:
\begin{equation}
\label{eq:clm1Induct}
\forall_{T, s_G \in \mathcal{S}_G, a} |Q_G(s_G, a) - Q_T(s_G, a)| \leq \sum_{t=0}^{T-1} \epsilon \gamma^{t},
\end{equation}

@@

We assume as our inductive hypothesis that:
\begin{equation*}
\forall_{s_G \in \mathcal{S}_G, a} |Q_G(s_G, a) - Q_{T-1}(\epQ(s_G), a)| \leq \sum_{t=0}^{T-2} \epsilon \gamma^t.
\end{equation*}

Consider a fixed but arbitrary state, $s_G \in \mathcal{S}_G$, and fixed but arbitrary action $a$.
We denote $\epQ(s_G)$ as $s_A$. 
By definition of $Q_{T}(s_A, a)$, $\mathcal{R}_A$, $\mathcal{T}_A$:
\begin{multline*}
Q_T(s_A, a) = \sum_{g \in G(s_A)}\omega(g)\ \times \\ 
 \left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'} Q_{T-1}(g', a')      \right].
\end{multline*}
Applying our inductive hypothesis yields:
\begin{multline*}
Q_T(s_A, a) \leq \sum_{g \in G(s_A)}\omega(g) \times \biggl[ R_G(g,a)\ + \\ \gamma \sum_{g' \in \mathcal{S}_G} T_G(g,a,g') \max_{a'}(Q_G(g', a') + \sum_{t=0}^{T-2} \epsilon \gamma^t) \biggr].
\end{multline*}
%&\leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \sum_{g \in X(s_A)}\omega(g)\left[ R_0(g,a) + \gamma \sum_{g' \in \mathcal{S}_G} T_0(g,a,g') \max_{a'}Q_0      \right]\\
Then,
\begin{equation*}
Q_T(s_A, a) \leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \sum_{g \in G(s_A)}\left[ \omega(g)\ Q_G(g,a)\right].
\end{equation*}
since all aggregated states have $Q$-values within $\epsilon$ of one another:
\begin{align*}
Q_T(s_A, a) \leq \gamma\sum_{t=0}^{T-2} \epsilon \gamma^t + \epsilon + Q_G(s_G, a). \\
\therefore\ \left| Q_{T}(s_A, a) - Q_G(s_G,a) \right| \leq \gamma\sum_{t=0}^{T-1}\epsilon \gamma^t
\end{align*}
Since $s_G$ and $s_A$ are arbitrary, we conclude Equation \ref{eq:clm1Induct}.

As $T \rightarrow \infty$, $\sum_{t=0}^{T-1} \epsilon \gamma^t \rightarrow \frac{\epsilon}{1-\gamma}$ by the sum of infinite geometric series and $Q_T \rightarrow Q_A$, Equation \ref{eq:clm1Induct} allows us to conclude Claim \ref{clm:closeQs}.\\

@@

Now, consider an approximate version of \citet{li2006towards}'s $\phi_{model}$, where states are aggregated together when their rewards and transitions are within $\epsilon$.
\bdefn{$\epM$}
We let $\epM$ define a type of abstraction that, for fixed $\epsilon$, satisfies:
\begin{multline}
\epM(s_1) = \epM(s_2) \rightarrow \\
\forall_a \left| \mcR_G(s_1, a) - \mcR_G(s_2, a)\right| \leq \epsilon\; \wedge\ \\
\forall_{s_A \in \mcS_A} \left|\sum_{{s_G}' \in G(s_A)} \left[\mcT_G(s_1, a, {s_G}') - \mcT_G(s_2, a,{s_G}')\right] \right| \leq \epsilon.
\end{multline}
\edefn

@@

We consider approximate abstractions derived from a multinomial distribution over $Q^*$ for similar reasons to our motivation in considering the Boltzmann distribution. Additionally, the multinomial distribution is appealing due to its simplicity.
\bdefn{$\epMu$}
We let $\epMu$ define a type of abstraction that, for fixed $\epsilon$, satisfies
\begin{multline}
\epMu(s_1) = \epMu(s_2) \rightarrow \\
\forall_{a} \left|\frac{Q_G(s_1,a)}{\sum_b Q_G(s_1,b)} - \frac{Q_G(s_1,a)}{\sum_b Q_G(s_1,b)}\right| \leq \epsilon.
\end{multline}
\edefn

We also assume that the difference in normalizing terms is bounded by some positive factor, $k \in \mathbb{R}$, of $\epsilon$:
\begin{equation}
\left |\sum_i Q_G(s_1,a_i) - \sum_j Q_G(s_2,a_j) \right | \leq k\epsilon.
\end{equation}
\begin{lma} When $S_A$ is created using a function of the $\epMu$ type, for some non-negative constant $k \in \mathbb{R}$:
\begin{equation}
\forall_{s \in S_M} V_G^{\pi^*_G}(s) - V_G^{\pi_{GA}}(s) \leq \frac{\frac{2\epsilon|\mathcal{A}|}{1-\gamma} + k \epsilon^2 + k}{(1-\gamma)^2}.
\end{equation}
\label{lma:mult_lemma}
\end{lma}
